Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-20 paper/paper.tex
pass on V.C

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial three months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion. The rationale was to
give attention to each engine more uniformly, enabling more fair
comparison across engines. We repeated the following routine until
Aug. 22, 2018. We sampled five warnings associated with the group of a
given engine, analyzed these warnings, and moved to the group of
warnings associated with the next engine.

>>>>

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial three months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \Fix{five} warnings in each group. A warning belongs to the
group of a given engine if only that engine manifests distinct
behavior, \ie{}, it produces a distinct output compared to others. We
separated in a distinct group the warnings for which two engines
diverge. The rationale for this methodology was to give attention to
each engine more uniformly, enabling more fair comparison across
engines.
